Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
Remove redundant continously.

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must be continuously satisfied.
   First, the Coq code needs to be continuously maintained for compatibility with its dependencies (the Coq proof assistant and several Coq packages from inside and outside \community) and reverse dependencies (\community projects that depend on it).
   Second, the book needs to be maintained consistent with respect to the evolutions of the Coq code.
   %\TODO[Pierre]{Find a better/simpler sentence about the project's structure?}
\end{abstract}

>>>>

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must be continuously satisfied.
   First, the Coq code needs to be maintained for compatibility with its dependencies (the Coq proof assistant and several Coq packages from inside and outside \community) and reverse dependencies (\community projects that depend on it).
   Second, the book needs to be maintained consistent with respect to the evolutions of the Coq code.
   %\TODO[Pierre]{Find a better/simpler sentence about the project's structure?}
\end{abstract}
